Required packages. Below packages/libraries needs to be installed and loaded before you run this script.

```{r echo=TRUE}
install.packages("knitr")
install.packages('ggplot2')
install.packages('data.table')
library(data.table)

```

# Reproducible Research: Peer Assessment 1

## Loading and preprocessing the data
```{r}
dt <- read.csv(file="activity.csv" )
dt$date_t <- as.Date(as.character(dt$date))
dtt <- as.data.table(dt)
dtSummary <- dtt[, list(totalStepseachDay = sum(steps), num = .N), by = date_t]
```

Histogram for total steps per dayl

```{r}
hist(dtSummary$totalStepseachDay , main="histogram : total steps per day")
abline(v= mean(dtSummary$totalStepseachDay, na.rm=TRUE), col="blue", lwd=3)
abline(v= median(dtSummary$totalStepseachDay, na.rm=TRUE), col="red", lwd=1)
legend(x = "topright", c( "Mean", "Median"),col = c("blue",  "red"),lwd = c(2, 2))

```


## What is mean total number of steps taken per day?
mean total number of steps taken per day :
```{r}
mean(dtSummary$totalStepseachDay , na.rm=TRUE)
```

Median value : 
```{r}
median(dtSummary$totalStepseachDay , na.rm=TRUE)
```


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
